\def \bookname {Analysis II}

\documentclass[13pt,a4paper]{report}

\usepackage[margin=1in]{geometry}
\usepackage{amsthm}
\usepackage{amsmath}

\theoremstyle{definition}

\newtheorem{lemma}{Lemma}[section]
\newtheorem{exercise}{Exercise}[section]
\newtheorem{solution}{Solution}[section]

\begin{document}
\chapter{Metric spaces}
\section{Definitions and examples}

\begin{lemma}\label{convergence_lemma_1}
Let $(x_n)^\infty_{n=m}$ be a sequence of real numbers, and let $x$ be another real number. Then
$(x_n)^\infty_{n=m}$ converges to $x$ if and only if $\lim_{n \rightarrow \infty}
d(x_n, x) = 0$.
\end{lemma}

\begin{exercise}
Prove Lemma \ref{convergence_lemma_1}.
\end{exercise}

\begin{solution}
By definition of limit, for any $\varepsilon > 0$ there exists an $N \ge m$ such that
$d(x_n, x) = |x_n - x| < \varepsilon$ for all $n \ge N$. This is exactly the definition
of convergence in previous book.
\end{solution}

\begin{exercise}
Show that the real line with the metric $d(x, y) := |x - y|$ is indeed a metric space.
(Hint: you may wish to review your proof of Proposition 4.3.3.)
\end{exercise}

\begin{solution} We verify the four properties listed in Definition 1.1.2
\begin{itemize}
    \item[1.] $d(x, x) = |x - x| = 0$.
    \item[2.] For all $x \ne y$, $d(x, y) = |x - y| > 0$.
    \item[3.] For all $x$ and $y$, $d(x, y) = |x - y| = |y - x| = d(y, x)$.
    \item[4.] For all $x, y$ and $z$, $d(x, y) = |x - y| = |x - z + z - y| \le
    |x - z| + |z - y| = d(x, z) + d(z, y)$.
\end{itemize}
\end{solution}

\begin{exercise}
Let $X$ be a set, and let $d: X \times X \rightarrow [0, \infty)$ be a function.
\begin{itemize}
    \item[(a)] Give an example of a pair $(X, d)$ which obeys axioms (bcd) of Definition 1.1.2,
    but not (a). (Hint: modify the discrete metric.)
    \item[(b)] Give an example of a pair $(X, d)$ which obeys axioms (acd) of Definition 1.1.2,
    but not (b).
    \item[(c)] Give an example of a pair $(X, d)$ which obeys axioms (abd) of Definition 1.1.2,
    but not (c).
    \item[(d)] Give an example of a pair $(X, d)$ which obeys axioms (abc) of Definition 1.1.2,
    but not (d). (Hint: try examples where $X$ is a finite set.)
\end{itemize}
\end{exercise}

\begin{solution} In general, setting $X$ to be a finite set and defining $d$ by specifying values
for all pairs of elements can produce a lot of metric spaces for each of the problem. For this
exercise to be more challenging, we try to avoid abusing this approach.
\begin{itemize}
    \item[(a)] Let $d$ be the metric such that for all $x, y \in X$, $d(x, y) = 1$. This is similar
    to the discrete metric except that $d(x, x) = 1$ so it does not obey (a).
    \item[(b)] Similar to (a), we can as well set $d(x, y) = 0$ for all $x, y \in X$.
    \item[(c)]
    \item[(d)] Let $X = \{ 1, 2, 3 \}$ and define $d(x, x) = 0$ for $x \in X$, $d(1, 2) = d(2, 1)
    = 1$, $d(2, 3) = d(3, 2) = 1$ and finally $d(1, 3) = d(3, 1) = 3$.
\end{itemize}
\end{solution}

\begin{exercise}
Show that the pair $(Y, d|_{Y \times Y})$ defined in Example 1.1.5 is indeed a metric space.
\end{exercise}

\begin{solution}
Each of the four properties remains after $d$ is restricted to $Y \subset X$ and is vacuous to
verify.
\end{solution}

\begin{exercise}\label{exercise_1_1_5}
Let $N \ge 1$, and let $a_1, a_2, \ldots, a_n$ and $b_1, b_2, \ldots, b_n$ be real numbers. Verify
the identity
    \begin{equation*}
    \Bigg(\sum_{i = 1}^n a_i b_i\Bigg)^2 + \frac{1}{2} \sum_{i = 1}^n \sum_{j = 1}^n
    (a_i b_j - a_j b_i)^2 = \Bigg(\sum_{i = 1}^n a_i^2 \Bigg) \Bigg(\sum_{j = 1}^n b_j^2 \Bigg)
    \end{equation*}
and conclude the \it{Cauchy-Schwarz inequality}
    \begin{equation*}
    \Bigg|\sum_{i = 1}^n a_i b_i \Bigg| \le \Bigg(\sum_{i = 1}^n a_i^2\Bigg)^{\frac{1}{2}}
    \Bigg(\sum_{j = 1}^n b_j^2\Bigg)^{\frac{1}{2}}
    \tag{(1.3)}
    \end{equation*}
Then use the Cauchy-Schwarz inequality to prove the \it{triangle inequality}
    \begin{equation*}
    \Bigg(\sum_{i = 1}^n (a_i + b_i)^2\Bigg)^{\frac{1}{2}} \le
    \Bigg(\sum_{i = 1}^n a_i^2\Bigg)^{\frac{1}{2}} +
    \Bigg(\sum_{j = 1}^n b_j^2\Bigg)^{\frac{1}{2}}
    \end{equation*}
\end{exercise}

\begin{solution}
\end{solution}

\begin{exercise}
Show that $({\bf R}^n, d_{l^2})$ in Example 1.1.6 is indeed a metric space. (Hint: use Exercise
\ref{exercise_1_1_5}.)
\end{exercise}

\begin{exercise}
Show that the pair $({\bf R}^n, d_{l^1})$ in Example 1.1.7 is indeed a metric space.
\end{exercise}

\begin{exercise}
Prove the two inequalities in (1.1). (For the first inequality, square both sides. For the second
inequality, use Exercise \ref{exercise_1_1_5}.)
\end{exercise}

\begin{exercise}
Show that the pair $({\bf R}^n, d_{l^\infty})$ in Example 1.1.9 is indeed a metric space.
\end{exercise}

\begin{exercise}
Prove the two inequalities in (1.2).
\end{exercise}

\begin{exercise}
Show that the discrete metric ${\bf R}^n, d_{\text{disc}}$ in Example 1.1.11 is indeed a metric
space.
\end{exercise}

\begin{exercise}
Prove Proposition 1.1.18.
\end{exercise}

\begin{exercise}
Prove Proposition 1.1.19.
\end{exercise}

\begin{exercise}
Prove Proposition 1.1.20. (Hint: modify the proof of Proposition 6.1.7.)
\end{exercise}

\begin{exercise}
Let
    \begin{equation*}
    X := \Bigg\{ (a_n)_{n = 0}^\infty : \sum_{n = 0}^\infty |a_n| < \infty \Bigg\}
    \end{equation*}
be the space of absolutely convergent sequences. Define the $l^1$ and $l^\infty$ metrics on this
space by
    \begin{equation*}

    \end{equation*}
\end{exercise}

\begin{exercise}
\end{exercise}

\end{document}
